Large and Infinitary Quotient Inductive-Inductive Types

### 2020-01-07 draft/paper.tex
compact intro

\input{abbrevs.tex}
\newcommand{\Lift}{\Uparrow}
\newcommand{\ToS}{\mathsf{ToS}}
\newcommand{\ext}{\triangleright}
\newcommand{\emptycon}{\scaleobj{.75}\bullet}
\newcommand{\Pii}{\Pi}
\newcommand{\appi}{\mathsf{app}}
\newcommand{\lami}{\mathsf{lam}}
\newcommand{\Pie}{\Pi^{\mathsf{ext}}}
\newcommand{\appe}{\mathsf{app^{ext}}}
\newcommand{\lame}{\mathsf{lam^{ext}}}
\newcommand{\Piinf}{\Pi^{\mathsf{inf}}}
\newcommand{\appinf}{\mathsf{app^{inf}}}
\newcommand{\laminf}{\mathsf{lam^{inf}}}
\newcommand{\appitt}{\mathop{{\scriptstyle @}}}
\newcommand{\Refl}{\mathsf{Refl}}
\newcommand{\IdU}{\mathsf{IdU}}
\newcommand{\ReflU}{\mathsf{ReflU}}
\newcommand{\Sig}{\mathsf{Sig}}
\newcommand{\ToSSig}{\mathsf{ToSSig}}
\newcommand{\Inductive}{\mathsf{Inductive}}

@@

Algebraic notions of models of type theories are examples for this. Here,
initial models represent syntax, and initiality corresponds to induction on
syntax. Several variants have been used, from contextual categories \cite{TODO} and
comprehension categories \cite{TODO} to categories with families \cite{TODO}, but all of these are
categories with extra structure.

The main motivation of the current paper is to generalize previously formalized
\cite{kaposi2019constructing} QIITs so that they accommodate more algebraic
formulations of type theories, and more aspects of their practical
metatheory. As a side effect of fulfilling this goal, infinitary QIITs such as
Cauchy real numbers \cite{TODO} are covered as well.

\subsection{Contributions}

We add the following features to QIITs:
\begin{enumerate}
  \item
  \textbf{Large constructors, large elimination} and algebras at different
  universe levels. Large elimination is routinely used in the metatheory of type
  theory, but it has not been presented explicitly in previous works about
  QIITs.
  \item
  \textbf{Infinitary constructors}. This allows infinitely branching
  trees. Also, the theory of QIIT signatures is itself large and infinitary,
  thus it can ``eat itself'', i.e.\ include its own signature and provide
  its own metatheory. This was not possible previously in
  \cite{kaposi2019constructing}, where only finitary QIITs were described. We
  exploit self-representation to bootstrap the model theory of signatures,
  without having to assume any pre-existing internal syntax.
  \item
  \textbf{Recursive equations}, i.e. equations appearing as assumptions
  of constructors. These have occurred previously in syntaxes of cubical type
  theories, as boundary conditions\cite{TODO}.
\end{enumerate}

@@

In Section \ref{sec:metatheory}, we describe the metatheory used in the rest of
the paper.  In Section \ref{sec:tos}, we introduce the theory of QIIT
signatures. TODO

\section{Metatheory}

%% We use extensional type theory as metatheory, extended with two features:
%% cumulative universes and a limited form of universe polymorphism.

%% The extensions are used to conveniently talk about large elimination and
%% algebras at different universe levels. For example, consider natural number
%% algebras at level $i$, given as the $\Sigma$-type $NatAlg_i :\equiv(Nat :
%% \Set_i)\times Nat\times(Nat \ra Nat)$. The initial such algebra is the set of
%% natural numbers, which is at level $0$, but in type theory we often want to
%% eliminate into larger $\Set_i$, for example when computing a $Nat$-indexed
%% family of types. Hence, we would like to

%% Cumulativity is used to reduce bureaucratic overhead of
%% handling algebras at different universe levels. For a simple example, consider
%% natural number algebras at level $i$, given as the $\Sigma$-type $NatAlg_i
%% :\equiv(Nat : \Set_i)\times Nat\times(Nat \ra Nat)$. The initial such algebra is
%% the set of natural numbers, which is at level $0$, but in type theory we often
%% want to eliminate into larger $\Set_i$, for example when computing a
%% $Nat$-indexed family of types.

%% We are working in a variant of extensional type theory with cumulative
%% universes, abbreviated as cETT.

%% In this paper we consider QII algebras at arbitrary finite levels, along with
%% large eliminations, where the initial algebra can be at a different level than
%% the target algebra. For a simple example, consider natural number algebras at
%% level $i$, given as the $\Sigma$-type $NatAlg_i :\equiv(Nat : \Set_i)\times
%% Nat\times(Nat \ra Nat)$. The initial such algebra is the set of natural numbers,
%% which is at level $0$, but in type theory we often want to eliminate into larger
%% $\Set_i$, for example when computing a $Nat$-indexed family of types. To support
%% convenient reasoning about levels in this paper, we need two features:
%% cumulativity and a way to quantify over finite levels. The former is essential
%% to reduce bureaucratic overhead, while the latter is required to talk about
%% arbitrary levels.

%% \subsection{Cumulativity}

%% %% Cumulativity makes handling of algebras and constructions at different levels
%% %% much easier. For example, given an algebra $\gamma : NatAlg_i$, cumulativity
%% %% allows us to also have $\gamma : NatAlg_{i+j}$. In a non-cumulative setting such
%% %% as Agda, we may only have for each type $A : \Set_i$ a type $\mathsf{Lift}_{i\,j}\,A :
%% %% \Set_{i+j}$ which is isomorphic to $A$ up to definitional equality.

%% In its most basic form, cumulativity requires that whenever $A : \Set_i$, and $i
%% < j$ then also $A : \Set_j$. We also need cumulativity for $\Sigma$ and function
%% types, in order to have cumulativity for QII algebras in general. For example,
%% we want to have $\gamma : NatAlg_j$ whenever $\gamma : NatAlg_i$ and $i < j$.

%% We use Sterling's cumulative algebraic type theory \cite{sterling2019algebraic} as basis for our metatheory. \todo{REASONS, revamp}

%% %% The reason is that it is the only rigorous
%% %% algebraic definition of cumulativity that we are aware of, and it also

%% %% The reason for this is twofold. First, it
%% %% supports the right kind of cumulativity for our purposes. Second, it is itself a
%% %% finitary QIIT with sort equations, hence this paper provides a model theory for
%% %% it

%% We extend the base theory with an extensional identity type, $\Sigma$-types and
%% the unit type. In \cite{sterling2019algebraic} a proof of canonicity is provided for the base
%% theory, which also includes a standard set-theoretic model. It is
%% straightforward to extend the canonicity proof to cover our additional type
%% formers.

%% From now on, we refer to this theory as cETT (cumulative extensional type
%% theory). When working in cETT, we use the following notation. We have
%% Russell-style universes $\Set_i$ indexed by natural numbers, dependent functions
%% as $(x : A)\ra B$, and dependent pairs as $(x : A)\times B$ with projections
%% $\proj1$ and $\proj2$. We sometimes leave parameters implicit in dependent
%% function types, e.g.\ write $\id : A \ra A$ instead of $\id : (A : \Set_i)\ra A
%% \ra A$. We also use subscripts as a field projection notation for iterated
%% pairs. For example, for $t : (A : \Set_i) \times (B : \Set_i) \times (f : A \ra
%% B)$, we use $B_t$ to denote the projection of the second component. Sometimes we
%% omit the subscript if it is clear from context. When we write ``exists'' in this
%% paper, we always mean chosen structure given by a $\Sigma$-type.

%% We write propositional equality as $t = u$, with $\refl_t$ for reflexivity. We
%% have equality reflection and uniqueness of identity proofs (UIP) for
%% $\blank=\blank$. The unit type is $\top$, with inhabitant $\tt$.

%% \todo{compactify cumulativity}

%% \begin{figure}
%% \begin{mathpar}
%%   \inferrule*[lab=universe formation]
%%              {i < j}
%%              {\Gamma \vdash \Set_i : \Set_{j}}

%%   \inferrule*[lab=function formation]
%%              {\Gamma \vdash A : \U_i \\ \Gamma,\,x : A \vdash B : \U_j}
%%              {\Gamma \vdash (x : A)\ra B : \U_{\max(i,j)} }

%%   \inferrule*[lab=$\Sigma$ formation]
%%              {\Gamma \vdash A : \U_i \\ \Gamma,\,x : A \vdash B : \U_j}
%%              {\Gamma \vdash (x : A)\times B : \U_{\max(i,j)} }

%%   \inferrule*[lab=unit formation]
%%              {\\}
%%              {\Gamma \vdash \top : \Set_i}

%%   \inferrule*[lab=equality formation]
%%              {\Gamma \vdash A : \Set_i \\ \Gamma \vdash t : A \\ \Gamma \vdash u : A}
%%              {\Gamma \vdash t = u : \Set_i}

%%   \inferrule*[lab=type lifting]
%%              {\Gamma \vdash A : \Set_i \\ i \leq j}
%%              {\Gamma \vdash\,\Lift_j A : \Set_{j}}

%%   \inferrule*[lab=lift composition]{}{\Lift_j (\Lift_i A) \equiv\,\,\Lift_{j} A}

%%   \inferrule*[lab=identity lift]{\Gamma \vdash A : \Set_i}{(\Lift_i A) \equiv\,A}

%%   \inferrule*[lab=term lifting]
%%              {}
%%              {\{t\,|\,\Gamma \vdash t : A\} \equiv \{t\,|\,\Gamma \vdash t :\,\,\Lift_i A\}}

%%   \inferrule*[lab=context lifting]
%%              {}
%%              {(\Gamma,\,x : A) \equiv (\Gamma,\,x :\,\,\Lift_i A)}

%%   \inferrule*[lab=universe lifting]{}{\Lift_j \Set_i \equiv \Set_i}

%%   \inferrule*[lab=function lifting]
%%              {}
%%              {\Lift_i((x : A)\ra B) \equiv (x :\,\Lift_i A)\ra\,\Lift_i B}

%%   \inferrule*[lab=pair lifting]
%%              {}
%%              {\Lift_i((x : A)\times B) \equiv (x :\,\Lift_i A)\,\times\Lift_i B}

%%   \inferrule*[lab=unit lifting]
%%              {}
%%              {\Lift_i\top \equiv \top}

%%   \inferrule*[lab=equality lifting]
%%              {}
%%              {\Lift_i(t = u) \equiv (t = u)}
%% \end{mathpar}

%% \caption{Some of the rules for lifting.}
%% \label{lifting}
%% \end{figure}

%% We also have a lifting operation on types, which introduces cumulativity. In
%% Figure \ref{lifting}, we include an excerpt of cETT's rules. We change
%% presentation slightly from Sterling: we use a $\U_{\max(i,j)}$ return type in
%% functions and pairs, instead of having both $A$ and $B$ types in the same
%% $\Set_i$, and we define type lifting with $i \leq j$ instead of $i < j$. These
%% changed rules are all derivable from the original ones. In general, we can
%% expect that lifting never impedes constructions, because it appropriately
%% computes out of the way.

%% Of special note is the \emph{term lifting rule}. It is a sort equation, an
%% equation between sets of terms, expressing that lifted types have exactly the
%% same terms as unlifted ones. This allows us to have $t :\,\,\Lift_j A$ whenever $t
%% : A$. Together with the universe lifting rule, this implies $A : \Set_{i+j}$
%% whenever $A : \Set_i$. Similarly, the lifting rules for functions and pairs give
%% us cumulativity for $NatAlg$. We derive a notion of subtyping:

%% \begin{definition}[Cumulative subtyping]
%%   For $A : \Set_i$, $i \leq j$ and $B : \Set_{j}$, we define $A \leq B : \Set_{j}$
%%   as $B =\,\,\Lift_j A$.  It follows from term lifting and equality reflection
%%   that whenever $A \leq B$ and $t : A$, then also $t : B$.
%% \end{definition}

%% \subsection{Universe Polymorphism}
%% \label{sec:universe_polymorphism}

%% For the sake of simplicity, we do not add this to cETT directly. Instead, we
%% quantify over levels in an unspecified metatheory \emph{outside} cETT. Hence, a
%% universe polymorphic cETT term is understood as a $\mathbb{N}$-indexed family of
%% terms. We reuse the notation of cETT functions for universe polymorphism, e.g.\ as
%% in the following function:
%% \[
%% \lambda\,i.\,\Set_i : (i : \mathbb{N})\ra \Set_{i+1}
%% \]
%% In this paper, we do not need to internalize level-polymorphic constructions,
%% so this setup is sufficient.

@@

\textbf{An identity type} $\Id : (a : \Tm\,\Gamma\,\U)\ra
\Tm\,\Gamma\,(\El\,a)\ra\Tm\,\Gamma\,(\El\,a)\ra \Tm\,\Gamma\,\U$, with $\Refl :
(t : \Tm\,\Gamma\,(\El\,a))\ra \Id\,a\,t\,t$, equality reflection and UIP.

@@

\begin{example}{Infinitary constructors}. The universe $\U$ is closed under
the $\Piinf$ function type, which allows such functions to appear in the domains
of $\Pii$ types. This allows, for example, a signature for trees branching with
arbitrary small sets. This is a signature at level 1, since we have $\Set_0$ as
a $\Pie$ domain type.
\begin{alignat*}{3}
& TreeSig :\equiv \\
& \hspace{1em}\emptycon \ext (Tree : \U)\\
& \hspace{1.35em}\ext (node : \Pie\,\Set_0\,(\lambda A.\,(A\,\arrinf\,Tree)\arri\El\,Tree))
\end{alignat*}
\end{example}

@@

\begin{example}{Recursive equations}. Again, the universe is closed under $\Id$, which allows us to write equations
in $\Pii$ domains. A minimal example:
\begin{alignat*}{3}
  & RecEqSig :\equiv\\
  & \hspace{0.5em}\emptycon\,\ext (A : \U) \ext (a : \El\,A)\ext (f : \Pii\,(x : A)\,(\Id\,A\,x\,a\arri\El\,A))
\end{alignat*}
More interesting (and complicated) examples are boundary conditions in various
cubical type theories\cite{TODO}. Note that our $\Id$ allows iterated equations
as well, but these are all trivial in the semantics, where we assume UIP.
\end{example}

@@

Our semantics has a ``type-theoretic'' flavor, which is inspired by the cubical
set model of Martin-Löf type theory by Bezem et al.\cite{cubical}. The core idea
is to avoid strictness issues by starting from basic ingredients which are already
strict enough. Hence, instead of modeling types as certain slices and
substitution by pullback, we model types as displayed categories with extra
structure, which naturally support strict reindexing.

@@

\section{Model Theory of the Theory of Signatures}

@@

\section{Term Models of QIITs}

>>>>

\input{abbrevs.tex}
\newcommand{\Lift}{\Uparrow}
\newcommand{\ToS}{\mathsf{ToS}}
\newcommand{\ext}{\triangleright}
\newcommand{\emptycon}{\scaleobj{.75}\bullet}
\newcommand{\Pii}{\Pi}
\newcommand{\appi}{\mathsf{app}}
\newcommand{\lami}{\mathsf{lam}}
\newcommand{\Pie}{\Pi^{\mathsf{ext}}}
\newcommand{\appe}{\mathsf{app^{ext}}}
\newcommand{\lame}{\mathsf{lam^{ext}}}
\newcommand{\Piinf}{\Pi^{\mathsf{inf}}}
\newcommand{\appinf}{\mathsf{app^{inf}}}
\newcommand{\laminf}{\mathsf{lam^{inf}}}
\newcommand{\appitt}{\mathop{{\scriptstyle @}}}
\newcommand{\Refl}{\mathsf{Refl}}
\newcommand{\IdU}{\mathsf{IdU}}
\newcommand{\ReflU}{\mathsf{ReflU}}
\newcommand{\Sig}{\mathsf{Sig}}
\newcommand{\ToSSig}{\mathsf{ToSSig}}
\newcommand{\Inductive}{\mathsf{Inductive}}
\newcommand{\Subtype}{\mathsf{Subtype}}
\newcommand{\subtype}{\mathsf{subtype}}

@@

Algebraic notions of models of type theories are examples for this. Here,
initial models represent syntax, and initiality corresponds to induction on
syntax. Several variants have been used, from contextual categories \cite{TODO}
and comprehension categories \cite{TODO} to categories with families
\cite{TODO}.

Real, surreal \cite{TODO} and ordinal numbers \cite{TODO} are examples of
\emph{infinitary} QIITs, which are represented as inductive trees which may
branch infinitely.

%% The main motivation of the current paper is to generalize previously formalized
%% \cite{kaposi2019constructing} QIITs so that they accommodate more algebraic
%% formulations of type theories, and more aspects of their practical
%% metatheory. As a side effect of fulfilling this goal, infinitary QIITs such as
%% Cauchy real numbers \cite{TODO} are covered as well.

\subsection{Contributions}
The current paper extends previously formalized QIITs
\cite{kaposi2019constructing}. We add the following features:
\begin{enumerate}
  \item
  \textbf{Large constructors, large elimination} and algebras at different
  universe levels. This fills in an important formal gap, since large
  elimination is routinely used in the metatheory of type theories, but it has
  not been but it has not been presented explicitly in previous works about
  QIITs.
  \item
  \textbf{Infinitary constructors}.
  Of special note here is that the theory of QIIT signatures is itself large and
  infinitary, thus it can ``eat itself'', i.e.\ include its own signature and
  provide its own metatheory. This was not possible previously in
  \cite{kaposi2019constructing}, where only finitary QIITs were described. In
  this paper we use self-representation to bootstrap the model theory of
  signatures, without having to assume any pre-existing internal syntax.
  \item
  \textbf{Recursive equations}, i.e. equations appearing as assumptions
  of constructors. These have occurred previously in syntaxes of cubical type
  theories, as boundary conditions\cite{TODO}.
\end{enumerate}

@@

In Section \ref{sec:metatheory}, we describe the metatheory used in the rest of
the paper. In Section \ref{sec:tos}, we introduce the theory of QIIT
signatures. In Section \ref{sec:semantics} we give categorical semantics to
signatures. In Section \ref{sec:tossig} we build model theory for the theory
of QIIT signatures. In Section \ref{sec:termmodels} we give a term model construction
of QIITs. We discuss related work and conclude in Sections \ref{TODO}

\section{Metatheory}
\label{sec:metatheory}

The metatheory used in this paper is extensional type theory, extended with a
form of cumulativity and an external notion of universe polymorphism. We refer
to this theory as cETT. We review the used features and notations
in the following.

\subsection{Core Extensional Theory}

We have Russell-style predicative universes $\Set_i$ indexed by natural
numbers, dependent functions as $(x : A)\ra B$, and dependent pairs as $(x :
A)\times B$ with projections $\proj1$ and $\proj2$. We sometimes leave
parameters implicit in dependent function types, e.g.\ write $\id : A \ra A$
instead of $\id : (A : \Set_i)\ra A \ra A$. We also use subscripts as a field
projection notation for iterated pairs. For example, for $t : (A : \Set_i)
\times (B : \Set_i) \times (f : A \ra B)$, we use $B_t$ to denote the projection
of the second component. Sometimes we omit the subscript if it is clear from
context. When we write ``exists'' in this paper, we always mean chosen structure
given by a $\Sigma$-type.

\todo{univ lvl for pi sigma}

%% Both for functions and $\Sigma$, the output universe level is given as the
%% maximum of the levels of the constituent type.

We write propositional equality as $t = u$, with $\refl_t$ for reflexivity. We
have equality reflection and uniqueness of identity proofs (UIP). The unit type
is $\top$, with inhabitant $\tt$.

\subsection{Cumulativity}

We use cumulative universes and cumulative subtyping as described
in \cite{timany2018cumulative}. Concretely, we have a $\blank\leq\blank$ subtyping
relation on types, and a corresponding subtyping rule.
\begin{mathpar}
  \inferrule*{i \leq j}
             {\Gamma \vdash \Set_i \leq \Set_j}

  \inferrule*{\Gamma,\,x : A \vdash B \leq B'}
             {\Gamma \vdash (x : A)\ra B \leq (x : A)\ra B'}

  \inferrule*{\Gamma\vdash A \leq A' \\ \Gamma,\,x : A \vdash B \leq B'}
             {\Gamma \vdash (x : A)\times B \leq (x : A') \times B'}

  \inferrule*{\\}
             {\Gamma \vdash A \leq A}

  \inferrule*{\Gamma \vdash A \leq B \\ \Gamma\vdash B \leq C}
             {\Gamma \vdash A \leq C}

  \inferrule*{\Gamma\vdash A \leq A' \\ \Gamma\vdash t : A}
             {\Gamma \vdash t : A'}
\end{mathpar}

Additionally, we have an internal type for $\blank\leq\blank$, analogously to
$\blank=\blank$ which is an internalization of definitional equality.
\begin{mathpar}
  \inferrule*{\Gamma \vdash A : \Set_i \\ \Gamma \vdash B : \Set_j}
             {\Gamma \vdash \Subtype\,A\,B : \Set_{\max(i, j)}}

  \inferrule*{\Gamma \vdash A \leq B}
             {\Gamma \vdash \subtype : \Subtype\,A\,B}

  \inferrule*{\Gamma \vdash t : \Subtype\,A\,B}
             {\Gamma \vdash A \leq B}
\end{mathpar}

We use cumulativity to reduce bureaucratic overhead when dealing with
constructions at different universe levels. The internal $\Subtype$ is used in
Section \ref{sec:termmodels} to prove cumulativity for general QIIT
algebras. For example, consider natural number algebras at level $i$, given as
the $\Sigma$-type $NatAlg_i :\equiv(Nat : \Set_i)\times Nat\times(Nat \ra
Nat)$. It follows from the subtyping rules that $i \leq j$ implies $NatAlg_{i}
\leq NatAlg_{j}$. However, cumulativity for arbitrary QIIT algebras does not
follow judgmentally; it can only be proven by induction on signatures, hence
the need for $\Subtype$.

Internal subtyping is not included in \cite{timany2018cumulative}, but it can be
justified by the set-theoretic model given there.

\subsection{Universe Polymorphism}
\label{sec:universe_polymorphism}

We need to talk about constructions at arbitrary universe levels. For the sake
of simplicity, we do not assume a notion of universe polymorphism in cETT,
instead we quantify over levels in an unspecified theory outside of cETT. Hence,
a universe polymorphic cETT term is understood as a $\mathbb{N}$-indexed family
of cETT terms. This is sufficient in this paper, since we do not need to
internalize level polymorphism.

We reuse the notation of cETT functions for
universe polymorphism, e.g.\ as in the following function:
\[
\lambda\,i.\,\Set_i : (i : \mathbb{N})\ra \Set_{i+1}
\]

@@

\textbf{An identity type} $\Id : (a : \Tm\,\Gamma\,\U)\ra
\Tm\,\Gamma\,(\El\,a)\ra\Tm\,\Gamma\,(\El\,a)\ra \Tm\,\Gamma\,\U$, with $\Refl :
(t : \Tm\,\Gamma\,(\El\,a))\ra \Tm\,\Gamma\,(\El\,(\Id\,a\,t\,t))$, equality reflection and UIP.

@@

\begin{example}{Infinitary constructors}. The universe $\U$ is closed under
the $\Piinf$ function type, which allows such functions to appear in the domains
of $\Pii$ types. This allows, for example, a signature for trees branching with
arbitrary small types. This is a signature at level 1, since we have $\Set_0$ as
a $\Pie$ domain type.
\begin{alignat*}{3}
& TreeSig :\equiv \\
& \hspace{1em}\emptycon \ext (Tree : \U)\\
& \hspace{1.35em}\ext (node : \Pie\,\Set_0\,(\lambda A.\,(A\,\arrinf\,Tree)\arri\El\,Tree))
\end{alignat*}
\end{example}

@@

\begin{example}{Recursive equations}. Again, the universe is closed under $\Id$, which allows us to write equations
in $\Pii$ domains. A minimal (and trivial) example:
\begin{alignat*}{3}
  & RecEqSig :\equiv\\
  & \hspace{0.5em}\emptycon\,\ext (A : \U) \ext (a : \El\,A)\ext (f : \Pii\,(x : A)\,(\Id\,A\,x\,a\arri\El\,A))
\end{alignat*}
More interesting (and complicated) examples for recursive equations are boundary
conditions in various cubical type theories \cite{TODO}. Note that our $\Id$
allows iterated equations as well, but these are all trivial in the semantics,
where we assume UIP.
\end{example}

@@

Our semantics has a ``type-theoretic'' flavor, which is inspired by the cubical
set model of Martin-Löf type theory by Bezem et al. \cite{cubical}. The core idea
is to avoid strictness issues by starting from basic ingredients which are already
strict enough. Hence, instead of modeling types as certain slices and
substitution by pullback, we model types as displayed categories with extra
structure, which naturally support strict reindexing.

@@

\section{Model Theory of the Theory of Signatures}
\label{sec:tossig}

@@

\section{Term Models of QIITs}
\label{sec:termmodels}
